---
title: "Embrace Your Fallibility"
subtitle: "" 
format: 
  html: 
    code-line-numbers: true
    fig-align: "center"
execute: 
  echo: false
editor_options: 
  chunk_output_type: console
bibliography: references.bib
---

```{r}
#| echo: false

exercise_number <- 1

```

```{r}
#| message: false

library(tidyverse)
library(gt)

source(here::here("src", "motivation.R"))

```

## Embrace Your Fallibility

### Why are we here?

The unifying interest of data scientists and statisticians is that **we want to learn about the world using data.**

Working with data has always been tough.

1.  Accurate
2.  Reproducible and auditable
3.  Collaborative

Working with data has **gotten tougher with time**. Data sources, methods, and tools have become more sophisticated. This leaves a lot of us stressed out because errors and mistakes feel inevitable and are embarrassing.

### What are we going to do?

Errors and mistakes are **inevitable**. It's time to [embrace our fallibility](https://www.nickeubank.com/wp-content/uploads/2016/06/Eubank_EmbraceYourFallibility.pdf).

In The Field Guide to Understanding Human Error [@dekker2014], the author argues that there are two paradigms:

1.  **Old-World View:** errors are the fault of individuals
2.  **New-World View:** errors are the fault of flawed systems that fail individuals

Errors and mistakes are **inevitable**. We want to use systems that don't fail us as statisticians and data scientists.

### How are we going to do this?

Errors and mistakes are **inevitable**. We want to adopt evidence-based best practices that minimize the probability of making an error and maximize the probability of catching an error when it inevitably happens.

[@parker] describes a process called opinionated analysis development.

We're going to adopt the approaches outlined in *Opinionated Analysis Development* and then actually implement them using modern data science tools.

Through years of applied data analysis, I've found these tools to be essential for creating analyses that are

1.  Accurate
2.  Reproducible and auditable
3.  Collaborative

## Why

Working with data has **gotten tougher with time**.

- Garden of forking paths and the credibility crisis. Transparency. 
- Data sets are way bigger
- Open source packages change



Even for simple analysis, we can ask ourselves an entire set of questions at the end of the analysis. @tbl-questions lists a few of these questions. 

```{r}
#| label: tbl-questions
#| tbl-cap: "Opinionated Analysis Development"

motivation |>
  select(`Question Addressed`) |>
  gt() |>
    tab_header(
    title = "Opinionated Analysis Development"
  ) |>
  tab_source_note(
    source_note = "Parker, Hilary. n.d. “Opinionated Analysis Development.” https://doi.org/10.7287/peerj.preprints.3210v1."
  )

```

## What

@tbl-features groups these questions in analysis features and suggests opinionated approaches to each question.

```{r}
#| label: tbl-features
#| tbl-cap: "Opinionated Analysis Development"

motivation |>
  select(-Tool, -Section) |>
  gt() |>
    tab_header(
    title = "Opinionated Analysis Development"
  )  |>
  cols_hide(`Analysis Feature`) |>
  tab_row_group(
    label = md("**Collaborative**"),
    rows = `Analysis Feature` == "Collaborative"
  ) |>  
  tab_row_group(
    label = md("**Accurate Code**"),
    rows = `Analysis Feature` == "Accurate Code"
  ) |>  
  tab_row_group(
    label = md("**Reproducible and Auditable**"),
    rows = `Analysis Feature` == "Reproducible and Auditable"
  ) |>
  tab_footnote(
    footnote = "This was originally 'Code Review'",
    locations = cells_body(columns = `Opinionated Approach`, rows = 7)
  )|>
  tab_source_note(
    source_note = md("**Source:** Parker, Hilary. n.d. “Opinionated Analysis Development.” https://doi.org/10.7287/peerj.preprints.3210v1.")
  )

```

## How

@tbl-tools lists specific tools we can use to adopt each opinionated approach. 

```{r}
#| label: tbl-tools
#| tbl-cap: "Opinionated Analysis Development"

motivation |>
  select(-Section) |>
  gt() |>
    tab_header(
    title = "Opinionated Analysis Development"
  )  |>
  cols_hide(`Analysis Feature`) |>
  tab_row_group(
    label = md("**Collaborative**"),
    rows = `Analysis Feature` == "Collaborative"
  ) |>  
  tab_row_group(
    label = md("**Accurate Code**"),
    rows = `Analysis Feature` == "Accurate Code"
  ) |>  
  tab_row_group(
    label = md("**Reproducible and Auditable**"),
    rows = `Analysis Feature` == "Reproducible and Auditable"
  ) |>
  tab_footnote(
    footnote = "This was originally 'Code Review'",
    locations = cells_body(columns = `Opinionated Approach`, rows = 7)
  )|>
  tab_footnote(
    footnote = "Added by Aaron R. Williams",
    locations = cells_column_labels(columns = Tool)
  ) |>  
  tab_source_note(
    source_note = md("**Source:** Parker, Hilary. n.d. “Opinionated Analysis Development.” https://doi.org/10.7287/peerj.preprints.3210v1.")
  )

```

BONUS STUFF

- Reproducible analyses are easy to scale
- Free web hosting
- Awesome output formats






## Roadmap

Finally, @tbl-roadmap outlines the structure of the rest of the day. 

```{r}
#| label: tbl-roadmap
#| tbl-cap: "Opinionated Analysis Development"

motivation |>
  filter(!is.na(Section)) |>
  select(-`Analysis Feature`) |>
  arrange(Section) |>
  gt() |>
    tab_header(
    title = "Opinionated Analysis Development"
  )  |>
  tab_footnote(
    footnote = "This was originally 'Code Review'",
    locations = cells_body(columns = `Opinionated Approach`, rows = 7)
  )|>
  tab_footnote(
    footnote = "Added by Aaron R. Williams",
    locations = cells_column_labels(columns = c(Tool, Section))
  ) |>  
  tab_source_note(
    source_note = md("**Source:** Parker, Hilary. n.d. “Opinionated Analysis Development.” https://doi.org/10.7287/peerj.preprints.3210v1.")
  )

```
